Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-25 wpe.tex
Liz is done

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven \emph{et al.} utilize the
relative entropy to quantify the difference in predictability between
two distributions: one evolved from a small ensemble of past
states using the known dynamical system, and the other the
asymptotic distribution. Our work quantifies the predictability of a
single observed time series using weighted permutation entropy and
makes no assumptions about the generating process.

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven \emph{et al.} utilize the
relative entropy to quantify the difference in predictability between
two distributions: one evolved from a small ensemble of past
states using the known dynamical system, and the other the
observed distribution. Our work quantifies the predictability of a
single observed time series using weighted permutation entropy and
makes no assumptions about the generating process.
